\propertitle

### 2019-07-10 maxNt_v5.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-07-10T10:12:32+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

%\newcommand*{\yx}{\bm{\yxv}}%subpop state
%\newcommand*{\yxs}{\sav{\yx}}%subpop av state
%\newcommand*{\yX}{\bm{\yXv}}%pop state
%\newcommand*{\yXf}{\av{\yX}}%pop av state
\newcommand*{\yaa}{\bm{\yav}}%subpop value
\newcommand*{\yaas}{\sav{\yaa\yaa}}%subpop av state
%\newcommand*{\yXXf}{\av{\yAA\yAA}}%subpop av state
\newcommand*{\ya}{\yav}%subpop av value
\newcommand*{\yAA}{\bm{\yAv}}%pop value
\newcommand*{\yA}{\yAv}%pop av value
%conditional assumptions
\newcommand*{\yH}{\varIota}
\newcommand*{\yD}{\varDelta}
\newcommand*{\yHa}{\varIota_\textrm{p}}
\newcommand*{\yHb}{\varIota_\textrm{s}}
\newcommand*{\yHc}{\varKappa}
\newcommand*{\yHd}{\varIota_\textrm{u}}
\newcommand*{\yHp}{\varIota'}
\newcommand*{\yHi}{\varIota''}
%Lagr multipliers
\newcommand*{\yg}{\bm{c}}
\newcommand*{\yc}{\widehat{\bm{c}}}
\newcommand*{\yL}{\bm{\lambda}}
\newcommand*{\yl}{\bm{l}}
\newcommand*{\yk}{z}
\newcommand*{\yK}{\zeta}
%entropies
\newcommand*{\ysh}{H}
\newcommand*{\ybu}{H_{\text{B}}}

@@

In \sect~\ref{sec:model} we mentioned that maximum-entropy distributions
are approximations to the full answers provided by the probability
calculus. For example we ask: what is the frequency distribution for the
total activity of the full network across the recorded bins? Several
frequency distributions are possible, each with a specific probability. The
maximum-entropy distribution is

@@

\begin{figure}[!p]
\centering
\includegraphics[width=\linewidth]{_scripts/MC_plot1000.pdf}%
\\[3em]%
\includegraphics[width=\linewidth]{_scripts/MC_samples1000.pdf}%
\caption{***}
\label{fig:comparisons_marginals}
\end{figure}
%mctests3.nb
%plot_mcfd_6mom_unif_afssd26_cok_tr_N1000_t50_L50_T0.333333333333333_s60000_a0

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-07-10T11:49:38+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

%\newcommand*{\yx}{\bm{\yxv}}%subpop state
%\newcommand*{\yxs}{\sav{\yx}}%subpop av state
%\newcommand*{\yX}{\bm{\yXv}}%pop state
%\newcommand*{\yXf}{\av{\yX}}%pop av state
\newcommand*{\yaa}{\bm{\yav}}%subpop value
\newcommand*{\yaas}{\sav{\yaa\yaa}}%subpop av state
%\newcommand*{\yXXf}{\av{\yAA\yAA}}%subpop av state
\newcommand*{\ya}{\yav}%subpop av value
\newcommand*{\yAA}{\bm{\yAv}}%pop value
\newcommand*{\yA}{\yAv}%pop av value
%conditional assumptions
\newcommand*{\yH}{\varIota}
\newcommand*{\yHa}{\varIota_\textrm{p}}
\newcommand*{\yHb}{\varIota_\textrm{s}}
\newcommand*{\yHc}{\varKappa}
\newcommand*{\yHd}{\varIota_\textrm{u}}
\newcommand*{\yHp}{\varIota'}
\newcommand*{\yHi}{\varIota''}
\newcommand*{\yI}{\varIota}
\newcommand*{\yD}{D}
%Lagr multipliers
\newcommand*{\yg}{\bm{c}}
\newcommand*{\yc}{\widehat{\bm{c}}}
\newcommand*{\yL}{\bm{\lambda}}
\newcommand*{\yl}{\bm{l}}
\newcommand*{\yk}{z}
\newcommand*{\yK}{\zeta}
%entropies
\newcommand*{\ysh}{H}
\newcommand*{\ybu}{H_{\text{B}}}

@@

In \sect~\ref{sec:model} we mentioned that maximum-entropy distributions
come from a zeroth-order Laplace approximation of the densities obtained
from the probability calculus. Zeroth-order means that we are simply
considering the mode of such densities. Let's be more concrete. Consider
the question: What is the relative-frequency distribution for the different
activity levels for the full-network, across the recorded bins? Call this
distribution $(\yFF_{\yA}) \defs \yF$: activity level $\yA$ appeared in
$T\,\yFF(\yA)$ out of $T$ time bins. We don't know $\yF$, and our
uncertainty about its possible values is a probability distribution
$\pf(\yF\|\yD\yI)$ conditional on data $\yD$ and prior knowledge $\yI$,
which we approximate with a continuous density
\begin{equation}
  \label{eq:density_F}
  \pf(\yF \| \yD \yI)\;\di\yF.
\end{equation}
Now consider the related question: What is the activity $\yA_{t}$ of the
full network at some specific time bin $t$? If we don't know the exact
sequence of activities during the recording then we don't know $\yA_{t}$;
if we know the frequency distribution $\yF$ of the activity levels, then
our probability for $\yA_{t}$ is $\yFF_{\yA_{t}}$, out of combinatorial
reasons. But if we are also uncertain about $\yF$, with
probability~\eqref{eq:density_F}, then our probability for $\yA_{t}$ by
marginalization is
\begin{equation}
  \label{eq:probability_AT}
  \pf(\yA_{t} \| \yD \yI) =
  \int \yFF_{\yA_{t}}\;   \pf(\yF \| \yD \yI)\;\di\yF.
\end{equation}

@@

\begin{figure}[!p]
\centering
\includegraphics[width=\linewidth]{_scripts/MC_plot1000.pdf}%
\\[3em]%
\includegraphics[width=\linewidth]{_scripts/MC_samples1000.pdf}%
\caption{***}
\label{fig:comparisons_marginals}
\end{figure}
% mctests3.nb
% mcfd_6mom_unif_afssd40st0np_cok_tr_N1000_t50_L50_T0.333333333333333_s60000_a15758.0500981316

\begin{figure}[!p]
\centering
\includegraphics[width=\linewidth]{_scripts/MC_plot5000.pdf}%
\\[3em]%
\includegraphics[width=\linewidth]{_scripts/MC_samples5000.pdf}%
\caption{***}
\label{fig:comparisons_marginals}
\end{figure}
% mctests3.nb
% mcfd_6mom_unif_afssd32s_cok_tr_N5000_t180_L50_T0.333333333333333_s25800_a329212306.071189
